Gaia DR2 view of the GD-1 stellar stream

### 2018-04-28 paper/gd1.tex
abstract tweaks

\begin{abstract}\noindent % trust me
Tidally-disrupted globular clusters are transformed into thin, dynamically-cold streams
of stars that are extremely valuable tracers of the large- and small-scale
distribution of matter in the Galaxy.
Most of such streams discovered in the Milky Way reside in its halo, and are therefore primarily sensitive to the distribution of dark matter.
We present a sample of highly-probable members of the longest cold stream, GD-1, selected on small parallaxes and retrograde proper motions provided by the \gaia\ mission, and \pans\ photometry consistent with an old and metal-poor population at a distance of $\sim10\,$kpc.
This selection extended the stream by $10^\circ$(?), revealed a possible location of the progenitor and mapped significant density variations along the stream in unprecedented detail.
In addition to several prominent gaps, for the first time we also find evidence of stream members off the main track.
No(?) secular formation mechanisms predict the existence of such spurs, but they are a natural result of a stream interaction with a massive perturber.
Based on the impulse approximation arguments, we estimate that the detected underdensity and the associated spur could have been induced by a perturbation of a $\sim10^7\rm M_\odot$(?) object.
Our model of GD-1 indicates that the stream crosses the Milky Way disk at a large radius, which puts the likely origin of the perturber beyond the stellar disk.
\end{abstract}

>>>>

\begin{abstract}\noindent % trust me
Tidally-disrupted globular clusters are transformed into thin, dynamically-cold streams
of stars that are extremely valuable tracers of the large- and small-scale
distribution of matter in the Galaxy.
Most of such streams discovered in the Milky Way reside in its halo, and are therefore primarily sensitive to the distribution of dark matter.
We present a sample of highly-probable members of the longest cold stream, GD-1, selected on small parallaxes and retrograde proper motions provided by the \gaia\ mission, and \pans\ photometry consistent with an old and metal-poor population at a distance of $\sim10\,$kpc.
This selection extended the stream by $10^\circ$(?), revealed a possible location of the progenitor and mapped significant density variations along the stream in unprecedented detail.
In addition to several prominent gaps, for the first time we also find evidence of stream members off the main track.
No(?) secular formation mechanisms predict the existence of such spurs, but they are a natural result of a stream interaction with a massive perturber.
Based on the impulse approximation arguments, we estimate that the detected underdensity and the associated spur could have been induced by a perturbation of a $\sim10^7\,\rm M_\odot$(?) object $\sim 0.5\,$Gyr ago.
Our model of GD-1 indicates that the stream crosses the Galactic plane at a large radius, which puts the likely origin of the perturber beyond the stellar disk.
\end{abstract}
